Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-05-01 paper/paper.tex
restoring intended meaning

\subsubsection{Self-training and the loss function}
Successful learning in brains and computer algorithms is challenging without a
defined learning goal \textemdash the \textit{loss function}.
The action $a$ chosen in state $s$ according to the policy matrix defined in
\eqref{eq:policy} yields a reward $r$ collected by the agent,
% (measured on their internal currency of worldly values ?),
after which the environment transitions to a new state $s' \in \mathcal S$.
% \textbf{XXX Please try to smoothen the previous sentence}
One such cycle yields a new \textit{experience} $e = (s,a,r,s')$.
Each cycle represents a behavior unit of the agent
and is recorded in replay memory buffer \textemdash which we hypothesize to be the
HC \textemdash, possibly discarding the oldest entries to make space:
$\mathcal D \leftarrow \text{append}(\mathcal D, e)$.

>>>>

\subsubsection{Self-training and the loss function}
Successful learning in brains and computer algorithms is not possible without a
defined learning goal \textemdash the \textit{loss function}.
The action $a$ chosen in state $s$ according to the policy matrix defined in
\eqref{eq:policy} yields a reward $r$ collected by the agent,
% (measured on their internal currency of worldly values ?),
after which the environment transitions to a new state $s' \in \mathcal S$.
% \textbf{XXX Please try to smoothen the previous sentence}
One such cycle yields a new \textit{experience} $e = (s,a,r,s')$.
Each cycle represents a behavior unit of the agent
and is recorded in replay memory buffer \textemdash which we hypothesize to be the
HC \textemdash, possibly discarding the oldest entries to make space:
$\mathcal D \leftarrow \text{append}(\mathcal D, e)$.
